\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{grey}

\usepackage[scale=0.80]{geometry}

\name{Ben}{Adams}
\title{\color{black}Software Engineer}
\phone[mobile]{+1.704.450.9433}
\email{adams.benjamin@pm.me}
\social[github]{AdamsBenjamin}
\social[linkedin]{benjamin-adams-211481105}

\begin{document}
\maketitle

\section{Employment}
% \cventry
%    {} % Years
%    {} % Title
%    {} % Employer
%    {} % Location, nullable
%    {} % inexplicably blank
%    {} % Description , nullable

\cventry
    {2021--2023}
    {Software Engineer II}
    {Ntrepid Corp}
    {Remote}
    {}
    {Coordinate with internal customers to integrate third-party data APIs into discoverability service.\newline{}
     Normalize external data to create large data archives.\newline{}
     Build and expand on queryability of data to ease discovery of points of interest.\newline{}
     Create isolated, reproducible application builds using Docker and Terraform.}

\cventry
    {2021--2021}
    {Teaching Assistant}
    {Trilogy LLC}
    {Remote}
    {}
    {Assist and guide students in learning and mastering the basics of web technologies.\newline{}
     Evaluate and offer feedback and guidance on student submissions.\newline{}
     Provide technical support for students in the setup and configuration of tools.}

\cventry
    {2019--2020}
    {Software Engineer II}
    {IBM (via Apex Systems)}
    {Charlotte, NC}
    {}
    {Maintain automation-focused Perl/CGI applications.\newline{}
     Replace Perl/CGI applications with Python-based Flask applications.\newline{}
     Work extensively with regex to transform internal messaging into customer-oriented notifications.}

\cventry
    {2018--2019}
    {Software Engineer I}
    {AT\&T (via Apex Systems)}
    {Charlotte, NC}
    {}
    {Provide services to coordinate physical asset management efforts.\newline{}
     Leverage Django and Celery to parse and validate spreadsheets.}

\section{Technical Skills}
\begin{itemize}
\itemindent.6in
    \item \emph{Languages}: Python, C, SQL, Bash, Rust, Javascript, Perl
    \item \emph{Libraries}: FastAPI, Flask, Celery, Numpy
    \item \emph{Tools}: Linux, Docker, Kubernetes, Terraform, AWS, Elastic, mypy, pytest, make
\end{itemize}

\section{Education}
\cventry
    {2012--2016}
    {Bachelor of Science in Computer Science}
    {Appalachian State University}
    {Boone, NC}
    {}
    {}

\end{document}
